\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-05-24 paper/manuscript.tex
updated tables with before/after/current info on files and filesizes

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 21:39:50 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lr}
		\hline
		File type & Occurrences \\ 
		\hline
		.pdf & 1371 \\ 
		.html & 819 \\ 
		.png & 210 \\ 
		.jpg & 131 \\ 
		.gif &  99 \\ 
		.js &  51 \\ 
		.PDF &  50 \\ 
		.aspx &  43 \\ 
		.doc &  35 \\ 
		.css &  32 \\ 
		.JPG &  26 \\ 
		.Net &  12 \\ 
		.xlsx &   6 \\ 
		.docx &   5 \\ 
		.ttf &   3 \\ 
		.xml &   3 \\ 
		.htm &   2 \\ 
		.woff &   2 \\ 
		.xls &   2 \\ 
		.asp &   1 \\ 
		.eot &   1 \\ 
		.GIF &   1 \\ 
		.ico &   1 \\ 
		.PNG &   1 \\ 
		.ppt &   1 \\ 
		.swf &   1 \\ 
		.txt &   1 \\ 
		\hline
	\end{tabular}
	\caption{File types in scraped websites} 
\end{table}

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Wed Feb 22 21:35:10 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrr}
		\hline
		Website & Files & Size (MB) \\ 
		\hline
		brownsvilletn.gov & 188 & 14328 \\ 
		www.centralpointoregon.gov & 150 & 137440 \\ 
		www.dedham-ma.gov & 603 & 212572 \\ 
		www.duncanok.gov &  84 & 47064 \\ 
		www.dutchessny.gov & 110 & 291376 \\ 
		www.ennistx.gov & 200 & 26244 \\ 
		www.greenvillenc.gov & 333 & 25732 \\ 
		www.romi.gov & 491 & 112584 \\ 
		www.trumbull-ct.gov & 787 & 191540 \\ 
		www.westonct.gov & 861 & 213140 \\ 
		\hline
	\end{tabular}
	\caption{Test websites} 
\end{table}

@@

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Tue May 23 19:28:26 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lrrr}
		\hline
		Filetype & current & before & after \\ 
		\hline
		& 51455 & 13866 & 19199 \\ 
		pdf & 9646 & 5489 & 7544 \\ 
		jpg & 5216 & 1988 & 3512 \\ 
		html & 3767 & 17842 & 17596 \\ 
		aspx & 2832 & 4356 & 3271 \\ 
		png & 2714 & 2327 & 3684 \\ 
		gif & 1068 & 664 & 1077 \\ 
		JPG & 478 & 182 & 263 \\ 
		1 & 443 &  61 &  54 \\ 
		css & 390 & 265 & 518 \\ 
		js & 350 & 255 & 468 \\ 
		htm & 264 & 295 & 256 \\ 
		docx & 203 & 106 & 120 \\ 
		doc & 167 &  70 & 130 \\ 
		asp & 161 & 201 & 211 \\ 
		svg &  87 &  55 &  69 \\ 
		php &  83 & 157 & 241 \\ 
		\hline
	\end{tabular}
	\caption{The most common file types in scraped websites} 
\end{table}

\begin{landscape}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Tue May 23 19:35:22 2017
\begin{table}[ht]
	\centering
	\footnotesize
	\begin{tabular}{lrrrrrrrrr}
		\hline
		Website & current\_size & current\_files & before\_size & before\_files & after\_size & after\_files & size\_change & files\_change & control\_change \\ 
		\hline
		attica-in.gov & 61988 & 1417 & 7528 & 164 & 55956 & 1390 & 7.43 & 8.48 & 0.00 \\ 
		bedford.in.us & 57628 & 560 & 27452 & 182 & 46388 & 525 & 1.69 & 2.88 & 0.00 \\ 
		cityofboonvilleindiana.com & 9848 & 110 & 16996 & 172 & 20784 & 229 & 1.22 & 1.33 & 0.00 \\ 
		frankfort-in.gov & 205368 & 2652 & 12208 & 242 & 138360 & 1077 & 11.33 & 4.45 & 0.00 \\ 
		warsaw.in.gov & 298440 & 2117 & 26844 & 539 & 360400 & 2036 & 13.43 & 3.78 & 0.00 \\ 
		www.bloomington.in.gov & 131128 & 2713 & 443360 & 14384 & 247096 & 9640 & 0.56 & 0.67 & 0.00 \\ 
		www.brazil.in.gov & 43056 & 845 & 34472 & 625 & 55152 & 1214 & 1.60 & 1.94 & 0.00 \\ 
		www.carmel.in.gov & 2270016 & 8727 & 1919344 & 5361 & 899900 & 2219 & 0.47 & 0.41 & 0.00 \\ 
		www.ci.auburn.in.us & 183296 & 1025 & 21444 & 345 & 23564 & 211 & 1.10 & 0.61 & 0.00 \\ 
		www.cityoffortwayne.org & 2136424 & 4378 & 266784 & 3582 & 233600 & 3018 & 0.88 & 0.84 & 0.00 \\ 
		www.cityofhobart.org & 722000 & 2463 & 44192 & 650 & 62660 & 1037 & 1.42 & 1.60 & 0.00 \\ 
		www.evansvillegov.org & 6345932 & 11844 & 290784 & 1281 & 1697224 & 6853 & 5.84 & 5.35 & 0.00 \\ 
		www.gary.in.us & 373888 & 1227 & 121812 & 485 & 157140 & 719 & 1.29 & 1.48 & 0.00 \\ 
		www.huntingburg-in.gov & 388680 & 2496 & 8644 & 213 & 375900 & 1953 & 43.49 & 9.17 & 0.00 \\ 
		www.jasperindiana.gov & 561968 & 4013 & 55900 & 460 & 439072 & 2224 & 7.85 & 4.83 & 0.00 \\ 
		www.lakestation-in.gov &  48 &   2 & 7724 &  84 & 257272 & 1097 & 33.31 & 13.06 & 0.00 \\ 
		www.linton-in.gov &  32 &   1 &  24 &   2 &  24 &   2 & 1.00 & 1.00 & 0.00 \\ 
		www.madison-in.gov & 531044 & 1848 & 36636 & 575 & 191624 & 1444 & 5.23 & 2.51 & 0.00 \\ 
		www.martinsville.in.gov & 46792 & 1463 & 71628 & 1052 & 80944 & 800 & 1.13 & 0.76 & 0.00 \\ 
		www.monticelloin.gov & 33656 & 753 & 18120 & 448 & 100680 & 2104 & 5.56 & 4.70 & 0.00 \\ 
		www.newhavenin.org & 84364 & 626 & 2524 &  86 & 6792 & 334 & 2.69 & 3.88 & 0.00 \\ 
		www.richmondindiana.gov & 250968 & 1042 & 217252 & 918 & 401672 & 2422 & 1.85 & 2.64 & 0.00 \\ 
		www.southbendin.gov & 1264076 & 4749 & 454456 & 3286 & 1424136 & 2562 & 3.13 & 0.78 & 0.00 \\ 
		connersvillecommunity.com & 170688 & 569 & 162316 & 815 & 187276 & 808 & 1.15 & 0.99 & 1.00 \\ 
		www.batesvilleindiana.us & 166564 & 2348 & 39592 & 496 & 95696 & 1310 & 2.42 & 2.64 & 1.00 \\ 
		www.cityofrisingsun.com & 994956 & 3311 & 321400 & 1268 & 80848 & 868 & 0.25 & 0.68 & 1.00 \\ 
		www.cityofrockport-in.gov & 12068 &  98 & 5148 &  16 & 12068 &  98 & 2.34 & 6.12 & 1.00 \\ 
		www.elkhartindiana.org & 1132828 & 2345 & 5588 & 123 & 6204 & 223 & 1.11 & 1.81 & 1.00 \\ 
		www.elwoodcity-in.org & 224412 & 765 & 5000 & 123 & 139692 & 517 & 27.94 & 4.20 & 1.00 \\ 
		www.indy.gov & 5726048 & 9675 & 6119260 & 10451 & 4984080 & 7981 & 0.81 & 0.76 & 1.00 \\ 
		www.northvernon-in.gov & 272016 & 403 & 3132 & 112 & 289336 & 416 & 92.38 & 3.71 & 1.00 \\ 
		www.winchester-in.gov & 364592 & 2480 & 6508 & 135 & 45488 & 567 & 6.99 & 4.20 & 1.00 \\ 
		\hline
	\end{tabular}
	\caption{Number of files and size of websites} 
\end{table}
\end{landscape}

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{llr}
		\hline
		Variable & Unit & Source \\
		\hline
		Population size & 1000 people & Census \\
		Population growth last 5 years & Percent & Census \\
		Type of economy (agriculture/industry/services) & ? & Census \\
		Economic performance (GDP?) & \$ & Census \\
		Party of mayor before election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
		Party of mayor after election & Rep/Dem/(Ind) & in.gov/sos/elections/ \\
		Change of party control & 0/1 & in.gov/sos/elections/ \\
		Presidential vote 2012 in county & Percent Rep & ? (but I have the data) \\
		Unemployment rate & Percent & Census \\
		Broadband speed & Avg. Mbps DL & broadbandmap.gov \\
		\hline
	\end{tabular}
	\caption{List of covariates} 
\end{table}
